Guarded Recursion in Agda via Sized Type

### 2019-04-30 code-oneclock-paper/types-abstract/abstract.tex
one clock motivation

>>>>

The decision to restrict the clock context of \GTT\ to contain at most
one clock variable was dictated by our choice to use Agda with sized
types as the metatheory. In Agda, it is possible to encode semantic
clock contexts containing multiple clocks as lists of sizes or as
functions from a finite interval of natural numbers into
sizes. However, Agda's support for sized types is tailored to types
depending on exactly one size, or on a finite but precise number of
sizes, which makes it cumbersome to work with types depending on clock
contexts containing an indefinite number of clocks.
